\section{Setting the stage}
\label{sec:xs}
In the following section we collect and define all ingredients needed for \cref{eq:fact1}.
As already said, DIS is given by
\begin{equation}
    e^-(k) + p(P) \to e^-(k') + X
\end{equation}
\fherror{copy DIS diagram from PDG}
where the four-momenta $k,P,k'$ belong to the incoming electron, the incoming proton and the outgoing electron respectively.
This allows us, first, to define four momentum of the exchanged photon
\begin{equation}
    q = k - k'
\end{equation}
and from there the set of four common variables:
\begin{align}
    s &= (k + P)^2 = \frac{Q^2}{xy} \label{eq:defshad} \\
    Q^2 &= - q^2\\
    x &= \frac{Q^2}{2 q\cdot P}\\
    y &= \frac{q\cdot P}{k \cdot P}
\end{align}
Note that \cref{eq:defshad} gives an explicit relation among these, thus we have only three independent and one dependent variable.
In practice, the invariant mass of the electron-proton system $s$ is fixed by the experimental setup, i.e.\ by the energy of the colliding particles.
Also the measurable range of $y$ is in practice limited by the experimental geometry.
DIS cross-sections are typically provided as double-differential cross-sections in $x$ and $y$.
Finally, it is convenient to define the mass squared of the system X recoiling against the scatter electron,
\begin{equation}
    W^2 = (P + q)^2 = Q^2\left(\frac 1 x - 1\right)
\end{equation}
\begin{tcolorbox}[title={DIS requirements}]
    We require $Q^2 \gg \LQCD^2$ (deep) and $W^2 \gg \LQCD^2$ (inelastic) to call a lepton-hadron scattering DIS.
\end{tcolorbox}

We can decompose the (double-differential) cross-section into a leptonic interaction and a hadronic interaction, yielding each a tensor in Minkowski space, $L_{\mu\nu}$ and $W_{\mu\nu}$ respectively.
Thus, we can write
\begin{equation}
    \frac{\dd[2] \sigma}{\dd x \dd y} = \frac{2\pi y \aem^2}{Q^4} L_{\mu\nu}W^{\mu\nu}
\end{equation}
where we have introduced the electro-magnetic coupling $\aem$, which appears once on the leptonic side and once on the hadronic side.
We can express the leptonic tensor using plain Quantum Electrodynamics (QED) and provide a decomposition of the hadronic tensor in terms of scalar functions.
Together, we obtain
\begin{equation}
    \frac{\dd[2] \sigma}{\dd x \dd y} = \frac{4\pi \aem^2}{xy Q^2} \left(\left(1 - y + \frac {y^2 x}{2}\right)F_2(x,Q^2) - \frac{y^2x}{2}F_L(x,Q^2)\right)
\end{equation}
where we have introduced the two common scalar functions, now called structure functions $F_2$ and $F_L$, which are often measured in experiments.
It is convenient to also define a third, linearly dependent structure function via
\begin{equation}
    2xF_1 (x,Q^2) = F_2(x,Q^2) - F_L(x,Q^2)\,.
\end{equation}
Keep in mind that the discussion so far is a major simplification of DIS and in \cref{sec:diverse} we reintroduce the main complexity.

Let us continue to collect the remaining ingredient for \cref{eq:fact1}:
\begin{itemize}
    \item The sum over partons $j$ includes quarks and gluons and we refine in \cref{sec:hq} how large the sum actually is.
    \item The parton momentum fraction $\xi = x/z$ is the fraction of the four momentum the parton carries with respect to its parent proton.
    \item The probability of such a configuration to occur is given by the PDF, i.e. $f_j(\xi,Q^2)\dd \xi$ is the probability to find a parton $j$ with momentum $\xi P$ inside a proton with momentum $P$ at an experiment performed at the scale $Q^2$.
    \item The integration over $z$ sums all configuration to generate the final state configuration.
\end{itemize}
Finally, the coefficient functions $\vb C(x,Q^2)$ are computable order-by-order in pQCD and thus can be decomposed as
\begin{equation}
    \vb C(x,Q^2) = \sum_{k=0} \alpha_s^k(Q^2) \vb C^{(k)}(x)\,.
\end{equation}
Note that the $Q^2$ dependency of $\vb C(x,Q^2)$ is fully captured by the strong coupling $\alpha_s(Q^2)$.
