In preparation to \cref{sec:sv,sec:hq} we need to review two main ingredients into pQCD: the strong coupling $\alpha_s(Q^2)$, \cref{eq:CpQCD}, and the PDFs $\vb f(\xi,Q^2)$, \cref{eq:fact1}.
Specifically, we need to remind ourselves on their scale dependency also referred to as evolution.
While the two objects obey very similar equations, the strong coupling $\alpha_s(Q^2)$ is conceptually simpler and, thus, we start with that.

\subsection{The strong coupling}
\label{sec:as}

The strong coupling $\alpha_s$ is directly linked to the coupling of the gluons to quarks,
\begin{equation}
    \mathcal L_\text{QCD} \supset g T_a \bar{\psi} \gamma^\mu A^a_\mu \psi, \qquad \alpha_s = \frac{g^2}{4\pi}
\end{equation}
and is the central object in pQCD around which we organize our perturbative series.
If one considers higher order corrections to the gluon-quark couplings, one encounters quickly divergencies of ultra-violet origin, i.e.\ for large loop momenta.
This forces the introduction of a regularization procedure, typically dimensional regularization, which eventually leads to a scale dependent definition of the renormalized strong coupling $\alpha_s(\mu_R^2)$.
The introduced scale, called renormalization scale $\mu_R$ henceforth, is an arbitrary scale, which is an artifact of our regularization procedure and which effectively represents a separation between perturbative and non-perturbative regimes.
However, the scale dependence of $\alpha_s(\mu_R^2)$ is rigorously predicted in pQCD, organizing the terms in such a way that within the requested accuracy any dependence of $\mu_R$ is cancelled.
Recall that the scale dependence can be computed once the Lagrangian $\mathcal L$ is defined and does not require any actual observable.

Eventually, we obtain the renormalization group equation (RGE) of the strong coupling,
\begin{equation}
    \mu_R^2 \dv{\alpha_s(\mu_R^2)}{\mu_R^2} = \beta(\alpha_s) = - \sum_{j=0}\beta_j\qty(\alpha_s(\mu_R^2))^{2+j} \label{eq:beta}
\end{equation}
which is also the definition of the beta function $\beta(\alpha_s)$.
The upper limit of the sum in \cref{eq:beta} defines the perturbative accuracy, to which all other objects in pQCD refer to which is left implicit here and in the rest of this work.

At LO accuracy we find
\begin{equation}
    \mu_R^2 \dv{\alpha_s(\mu_R^2)}{\mu_R^2} = - \beta_0 \qty(\alpha_s(\mu_R^2))^2, \qquad \beta_0 = \frac{11 C_A - 2 n_f}{12\pi} \label{eq:LObeta}
\end{equation}
where we used the second Casimir constant of the adjoint representation $C_A = N_c = 3$ and the number of active flavors $n_f$, discussed in \cref{sec:hq}.
In this specific case we can solve \cref{eq:LObeta} and obtain
\begin{equation}
    \alpha_s^\text{LO}(\mu_R^2) = \frac{\alpha_s(\mu_{R,0}^2)}{1 + \alpha_s(\mu_{R,0}^2)\beta_0\ln(\mu_R^2/\mu_{R,0}^2)} \label{eq:LOalphas}
\end{equation}
for a given boundary condition $\alpha_s(\mu_{R,0}^2)$ at the scale $\mu_{R,0}^2$.
Recall, that \cref{eq:LOalphas} has not two free parameters, $\mu_{R,0}$ and $\alpha_s(\mu_{R,0})$ as one would naively think, but only one $\LQCD$ (see \cref{box:LOalphas}).
Also remember that $\LQCD$ corresponds to the pole in \cref{eq:LOalphas} and pQCD only makes sense above that scale, $\mu_R > \LQCD$.
Moreover, in practice it is often convenient to rewrite \cref{eq:beta} in terms of $t_R = \ln(\mu_R^2/\mu_{R,0}^2)$.

Now, coming back to the title of this section, note that \cref{eq:LOalphas} is a resummation:
\begin{equation}
    \alpha_s^\text{LO}(\mu_R^2) = \alpha_s(\mu_{R,0}^2) \sum_{k=0}^\infty \qty(-\alpha_s(\mu_{R,0}^2)\beta_0\ln(\mu_R^2/\mu_{R,0}^2))^k \label{eq:LOalphasresum}
\end{equation}
i.e.\ it collects an infinite tower of logarithms, here $\ln(\mu_{R,0}^2/\mu_R^2)$, into a compact expression, \cref{eq:LOalphas}.
Since $\mu_{R,0}$ is an arbitrary scale, often chosen to coincide with the mass of the $Z$ boson $\mu_{R,0}=m_Z$, it is basically always required to perform the resummation and use \cref{eq:LOalphas}.
However, in some situations, to be discussed in \cref{sec:sv}, we need \cref{eq:LOalphas} truncated to a finite order, i.e.\ unraveling \cref{eq:LOalphasresum}, and we get
\begin{equation}
    \alpha_s^\text{LO}(\mu_R^2) = \alpha_s(\mu_{R,0}^2) - \qty(\alpha_s(\mu_{R,0}^2))^2\beta_0\ln(\mu_R^2/\mu_{R,0}^2) + \ldots \label{eq:LOalphasexp}
\end{equation}
While for the special case $\mu_{R,0} = \mu_R$ we need to be consistent of course and we thus find that $\alpha_s^\text{LO}(\mu_R^2)$ is $\alpha_s(\mu_{R,0}^2)$ at the LO truncation, we note that they differ by higher order terms.
\Cref{eq:LOalphasexp} is the first, simplest case of a perturbative expansion of a resummed expression, \cref{eq:LOalphas}, and can also be obtained by using the Taylor expansion of $\alpha_s(\mu_R^2)$ around $\mu_{R,0}^2$ together with \cref{eq:LObeta}.
In other words, \cref{eq:LOalphasexp} is a perturbative expansion of \cref{eq:LOalphas} in powers of $\alpha_s(\mu_{R,0}^2)$.
Note that \cref{eq:LOalphasresum} has a finite radius of convergence (as all geometric series) and that is also reflected in \cref{eq:LOalphas} by the pole $\LQCD$.

Starting from NLO accuracy the RGE, e.g.\ in this specific case given by
\begin{equation}
    \mu_R^2 \dv{\alpha_s(\mu_R^2)}{\mu_R^2} = - \beta_0 \qty(\alpha_s(\mu_R^2))^2 - \beta_1 \qty(\alpha_s(\mu_R^2))^3\,, \label{eq:NLObeta}
\end{equation}
can no longer be solved exactly with elementary functions.
However, it is still possible to find an analytic solution which solves \cref{eq:NLObeta} at the requested accuracy, i.e.\ in this case NLO (see \cref{box:NLOalphas}).
This solution still performs a resummation, as we have to, but it only collects the so-called next-to-leading logarithms (NLL) (see \cref{box:NLOalphasLL}).
Note that the RGE has a given perturbative accuracy, e.g.\ NLO, but the solution has a given logarithmic accuracy, e.g.\ NLL, however, in the common language one often just uses only the former.

A completely different way to solve \cref{eq:NLObeta} is using numerical tools instead.
We refer to the literature on how to implement a specific solution in practice and remain here just with the fact that it is a complicated problem on its own, which has no unique solution and for which approximations are mandatory.
\begin{conclusionbox}[label={box:RGE}]{Solution of RGE}
    \begin{itemize}
        \item The LO RGE of the strong coupling, \cref{eq:LObeta}, can be solved exactly, \cref{eq:LOalphas}
        \item The RGE of the strong coupling at higher orders, e.g.\ \cref{eq:NLObeta}, can not be solved exactly and one needs to choose a solution method
    \end{itemize}
\end{conclusionbox}
Any proper solution of the RGE must solve the RGE itself at the requested accuracy else it is not a solution, but they can and do differ by terms beyond - we refer to the uncertainty which is associated with this freedom as Missing Higher Order Uncertainty (MHOU).
Truncating the perturbative series is a fundamental part of pQCD and thus we are always bound to the accuracy which we request at the beginning.
While in many simple application MHOU are often neglected they are an important ingredient in modern PDF fits~\cite{NNPDF:2024dpb} and in \cref{sec:sv} we demonstrate one possible way to estimate them.

\subsection{DGLAP}
\label{sec:DGLAP}

For PDFs $\vb f(\xi, \mu_F^2)$ the situation is essentially the same as for the strong coupling $\alpha_s(\mu_R^2)$, except the latter is just a number and the former are a set of functions.
The scale dependence is a again predicted by pQCD, but now we need an arbitrary physical observable to do so.
The specific observable does not matter since PDFs are universal, but due to the linear dependence on PDF and the \enquote{simplicity} of fully inclusive DIS it often serves as reference case.
The arbitrary scale that is introduced in the regularization procedure, typically called collinear factorization, is referred to as factorization scale $\mu_F$ henceforth.

Eventually, we obtain the RGE of PDFs, often referred to as DGLAP equation named after the researchers who established it~\cite{Altarelli:1977zs,Gribov:1972ri,Dokshitzer:1977sg},
\begin{equation}
    \mu_F^2 \dv{\vb f(\xi,\mu_F^2)}{\mu_F^2} = \qty(\vb P (\mu_F^2) \otimes \vb f(\mu_F^2))(\xi) = \sum_{j=0} \qty(\alpha_s(\mu_F^2))^{1+j} \qty(\vb P^{(j)} \otimes \vb f(\mu_F^2))(\xi) \label{eq:DGLAP}
\end{equation}
where $\vb P (y, \mu_F^2)$ is the matrix of Altarelli-Parisi splitting functions.
Note that the upper limit of the sum in \cref{eq:DGLAP} must be set to the requested perturbative accuracy, i.e.\ consistent with \cref{eq:LObeta}.

When attempting to solve \cref{eq:DGLAP} we must worry about the two complications in PDFs with respect of the strong coupling.
First, since PDFs are a vector and thus the Altarelli-Parisi splitting functions are combined in a matrix $\vb P$, we need to worry about non-commutativity.
Indeed, while at LO accuracy we only have a single matrix $\vb P^{(0)}$, which trivially commutates with itself, starting from NLO we encounter a second matrix $\vb P^{(1)}$, which does not commutate with the former.
Second, at any fixed scale PDFs are a function of the momentum fraction $\xi$ and, moreover, the right-hand-side of \cref{eq:DGLAP} features an integral (with the definition of the convolution $\otimes$ in \cref{eq:fact1,eq:fact2}).

To overcome the second problem, one possibility is to apply an integral transformation, the so-called Mellin transformation, defined by
\begin{align}
    \vb{\tilde f}(N,\mu_F^2) &= \int\limits_0^1 \dd \xi\,\xi^{N-1} \vb f(\xi,\mu_F^2) \label{eq:Mellinf} \\
    \gamma(N,\mu_F^2) &= \int\limits_0^1 \dd y\,y^{N-1} \vb P(y,\mu_F^2) \label{eq:Mellinad}
\end{align}
where the Mellin-transformed splitting functions $\gamma$ are often referred to as anomalous dimensions.
Inserting \cref{eq:Mellinf,eq:Mellinad} into \cref{eq:DGLAP} yields a \enquote{simple} first order differential equation as convolutions turn into ordinary products and which can be solved by a \enquote{simple} exponentiation.
However, in practice PDFs are mostly needed in momentum fraction space, $\vb f(\xi,\mu_F^2)$, and not in Mellin space, $\vb{\tilde f}(N,\mu_F^2)$, thus if we use the Mellin transform, we must also use its inverse transformation.

We can write the general solution to \cref{eq:DGLAP} in terms of an Evolution Kernel Operator (EKO)~\cite{Candido:2022tld} $\vb E$,
\begin{equation}
    \vb f (\xi,\mu_F^2) = \qty(\vb E(\mu_F^2 \leftarrow \mu_{F,0}^2) \otimes \vb f(\mu_{F,0}^2))(\xi)\,, \label{eq:EKO}
\end{equation}
but we skip spelling out an explicit solution here and refer to the literature instead~\cite{Candido:2022tld}.
The important part for us is that the operator (which is almost an exponential) again captures a resummation, in this case of $\ln(\mu_F^2/\mu_{F,0}^2)$.
Again, we can perform a perturbative expansion of the LO resummed solution to see the logarithm explicitly,
\begin{equation}
    \vb f^\text{LO}(\xi,\mu_F^2) = \vb f(\xi,\mu_{F,0}^2) + \alpha_s(\mu_{F,0}^2) \ln(\mu_F^2/\mu_{F,0}^2) \qty(\vb P^{(0)} \otimes \vb f(\mu_{F,0}^2))(\xi) + \ldots \label{eq:LOPDFexp}
\end{equation}
and starting from NLO accuracy, we face the same issues as for the strong coupling and \cref{box:RGE} applies in the same way.
