We now attempt to address a problem we first see in \cref{sec:resum}: Missing Higher Order Uncertainty (MHOU).
We repeat: the truncation of the perturbative series is a fundamental part of our framework and we are bound to it.
The naive solution of just computing the next higher correction is not a solution, as we would face the problem just again there.
Thus the task is to get an estimate of the missing terms based on current knowledge, which by definition is an ill-posed problem.
Several possible strategies have been suggested in the literature~\cite{NNPDF:2024dpb,Lim:2024nsk,Tackmann:2024kci,Kassabov:2022orn,Bonvini:2020xeo,Cacciari:2011ze,Duhr:2021mfd,Ghosh:2022lrf}, which are based on resummation of specific variables and/or statistical arguments.

From the practical point of view as a PDF fitter, however, there is one big problem with many of the proposed algorithms: they only work for some specific set of observables and require a detailed analysis of the kinematics.
Thus, we review here the most common approach to estimate MHOU, which can be rigorously derived in pQCD and applied to any observable: scale variations.
On the other side, especially in recent years, scale variations have been challenged as suitable tool, due to the inherent arbitrariness and the lack of statistical interpretation (see \cref{sec:svdiscussion}).
For now we focus on their practical implementation in DIS.

\subsection{Renormalization scale}
\label{sec:rensv}

We start again from the simpler case of the renormalization scale $\mu_R$ associated with the strong coupling $\alpha_s(\mu_R^2)$ via the RGE, \cref{eq:LObeta}.
As we say above, the renormalization scale captures the ultra-violet divergencies, which arise, e.g., from self-energy diagrams and which are thus associated with the partonic diagram itself.
Moreover, as we see from \cref{eq:CpQCD}, we expand the partonic coefficient functions in powers of the strong coupling.
\begin{conclusionbox}{Renormalization scale dependence}
    The renormalization scale dependence is captured by the partonic coefficient function $\vb C(z,Q^2,\mu_R^2)$.
\end{conclusionbox}
Since we have to choose something for the arbitrary scale $\mu_R$ and we only have a single scale available, the virtuality $Q^2$, we start by setting them equal to each other $\mu_R^2 = Q^2$, which is also the implicit choice in \cref{eq:fact1}.
We then need to find a way to estimate the missing terms in $\vb C(z,Q^2,\mu_R^2=Q^2)$, i.e.\ something that is identical at the requested perturbative accuracy, but differs from it beyond.
This can be achieved by using \cref{eq:LOalphasexp} together with a suitable redefinition of the perturbative coefficients of the partonic coefficient function $\vb C^{(j)}(z)$.
Specifically, we require
\begin{equation}
    \vb C(z,Q^2,\mu_R^2) = \vb C(z,Q^2,\mu_R^2=Q^2)\qty(1 + \order{\alpha_s(Q^2)})
\end{equation}
with
\begin{equation}
    \vb C(z,Q^2,\mu_R^2) = \sum_{j=0} \qty(\alpha_s(\mu_R^2))^j \vb C^{(j)}(z,\ln(\mu_R^2/Q^2)) \,. \label{eq:CbarRpQCD}
\end{equation}
Before we continue with deriving explicit expressions for $\vb C^{(j)}(z,\ln(\mu_R^2/Q^2))$ some comments are in order:
\begin{itemize}
    \item $\vb C(z,Q^2)$ in \cref{eq:fact1} is an abbreviation of $\vb C(z,Q^2,\mu_R^2=Q^2)$ and $\vb C^{(j)}(z)$ of $\vb C^{(j)}(z,\ln(\mu_R^2/Q^2)=0)$
    \item in \cref{eq:CbarRpQCD} $\mu_R$ has its intended meaning: it is the scale of the strong coupling
    \item from \cref{sec:as} we know $\alpha_s(\mu_R^2)$ is a pure resummation of logarithms, thus $\vb C^{(j)}$ may only depend on $\ln(\mu_R^2/Q^2)$
    \item $\vb C^{(j)}(z,0)$ can be computed from diagrams by assuming explicitly $\mu_R = Q$ there
\end{itemize}

We now derive the explicit next-to-next-to-leading order (NNLO) expression for fully inclusive DIS.
In particular, we recall that LO is given by $\vb C^{(0)}(z)$, i.e.\ proportional to $\qty(\alpha_s(Q^2))^0$ in \cref{eq:CpQCD}, NLO is given by $\vb C^{(1)}(z)$ proportional to $\qty(\alpha_s(Q^2))^1$, and NNLO by $\vb C^{(2)}(z)$ proportional to $\qty(\alpha_s(Q^2))^2$.
Moreover, we assume that the coefficient functions at the central scale $\mu_R=Q$ are known and we can write \cref{eq:CpQCD} up to NNLO
\begin{equation}
    \vb C(z,Q^2) = \vb C^{(0)}(z) + \alpha_s(Q^2) \vb C^{(1)}(z) + \qty(\alpha_s(Q^2))^2 \vb C^{(2)}(z) \label{eq:CNNLO}
\end{equation}
Expanding \cref{eq:CbarRpQCD} up to the same accuracy we get
\begin{align}
    \vb C(z,Q^2,\mu_R^2) &= \vb C^{(0)}(z,\ln(\mu_R^2/Q^2)) + \alpha_s(\mu_R^2) \vb C^{(1)}(z,\ln(\mu_R^2/Q^2)) \nonumber\\
    &\hspace{20pt} + \qty(\alpha_s(\mu_R^2))^2 \vb C^{(2)}(z,\ln(\mu_R^2/Q^2)) \label{eq:CbarRNNLO}
\end{align}
We are now left with the task to make \cref{eq:CNNLO} and \cref{eq:CbarRNNLO} perturbatively equivalent, and although we are considering NNLO the equivalence must hold at any lower order.
Thus, we can first consider LO $\vb C^{(0)}$: since there is no dependency on the strong coupling in the first place, the scale-varied coefficient function may not depend on the renormalization scale and we find
\begin{equation}
    \vb C^{(0)}(z,\ln(\mu_R^2/Q^2)) = \vb C^{(0)}(z)\,.
\end{equation}
Starting from NLO an explicit dependency on the strong coupling appears, however, from \cref{eq:LOalphasexp} we know that the two choices, $\alpha_s(Q^2)$ and $\alpha_s(\mu_R^2)$ differ by higher order terms.
Specifically, we have
\begin{equation}
    \alpha_s(Q^2) = \alpha_s(\mu_R^2) + \order{\qty(\alpha_s(\mu_R^2))^2} \qq{and} \alpha_s(\mu_R^2) = \alpha_s(Q^2) + \order{\qty(\alpha_s(Q^2))^2}
\end{equation}
Thus, if \cref{eq:CNNLO} and \cref{eq:CbarRNNLO} have to be the same up to $\order{\qty(\alpha_s(Q^2))^2}$, we find
\begin{equation}
    \vb C^{(1)}(z,\ln(\mu_R^2/Q^2)) = \vb C^{(1)}(z)\,.
\end{equation}
Since we are here interested in the perturbative equivalence, we must use the perturbative expansion of the evolution.

Note that with this identification \cref{eq:CNNLO} and \cref{eq:CbarRNNLO} (truncated to NLO) are not the same in practice, they are only perturbative equivalent.
In any actual calculation with $\mu_R\neq Q$ also $\alpha_s(\mu_R^2)$ and $\alpha_s(Q^2)$ are different: they differ by an amount which is beyond our fixed-order framework and if that difference is \enquote{small} depends on the actual values of the strong coupling of the respective scales.
However, with that we achieve the main purpose of this game: we generate some higher order terms, which we can then use to estimate MHOUs.

Starting from NNLO we see that the matching becomes non-trivial.
In the case at hand we can insert \cref{eq:LOalphasexp} into \cref{eq:CNNLO} (with the choice $(\mu_R,\mu_{R,0})\to (Q,\mu_R)$) and re-expand in powers of $\alpha_s(\mu_R^2)$ as requested.
We find
\begin{equation}
    \vb C^{(2)}(z,\ln(\mu_R^2/Q^2)) = \vb C^{(2)}(z) + \beta_0 \ln(\mu_R^2/Q^2) \vb C^{(1)}(z)\,, \label{eq:CbarRimpl}
\end{equation}
so the scale-varied coefficient function receives a correction from a lower-order coefficient function.

Let us take a step back and review the general features.
\begin{conclusionbox}[label={box:svren}]{Renormalization scale variation}
    Renormalization scale-varied coefficient functions
    \begin{itemize}
        \item can always be computed a posteriori from their non-scale-varied counterparts
        \item are a linear combination of their lower order non-scale-varied counterparts
        \item are derived by re-expanding the strong coupling in the perturbative sum up to the required perturbative accuracy
    \end{itemize}
\end{conclusionbox}
We also know that the dependency on the scale variation $\ln(\mu_R^2/Q^2)$ must be a polynomial dependence since the running of strong coupling is a pure resummation of this logarithm.
By re-expanding we mean a Taylor expansion of the strong coupling at the default scale, here $\alpha_s(Q)$, in terms of the value at the renormalization scale, $\alpha_s(\mu_R^2)$.
For computing the strong coupling at any scale $\alpha_s(\mu_R^2)$ we must use the required perturbative accuracy, but for deriving the scale-varied coefficient functions we only need one order less.
In the special case of fully inclusive DIS, which has no dependence on the strong coupling at LO, we even need only two orders lower then the coefficient functions.

For the sake of correcting \cref{eq:fact3}, we can improve it by writing
\begin{equation}
    \sigma(x,Q^2,\mu_R^2) = \qty(\vb C^T(Q^2,\mu_R^2) \otimes \vb f(Q^2))(x) \,.
\end{equation}

\subsection{Factorization scale}

As in \cref{sec:DGLAP} the general algorithm repeats for the factorization scale $\mu_F$, which is the intrinsic scale of PDFs, except everything is more complicated.
However, it is not only more complicated because PDFs are a set of function, but also because the PDF explicitly appears in \cref{eq:fact1}.
This implies, that the factorization scale dependence is not only be captured by the coefficient function, in contrast to the renormalization scale.
In particular, the factorization scale captures collinear divergencies, which arise in diagrams, and re-attributes them to the PDF, thus there is a direct connection between the two.
Recall our main goal here: we want to estimate MHOU by generating higher order terms and we simply have more freedom here to do so.
In order to simplify the discussion we explicitly neglect renormalization scale variations for the moment.

The most common way to deal with factorization scale variation is to directly modify the coefficient functions, as in the case for \cref{eq:CbarRpQCD}, and we refer to this choice as \enquote{factorization scale variation scheme C}~\cite{NNPDF:2024dpb}.
Specifically, we make a similar ansatz and write
\begin{equation}
    \sigma(x,Q^2,\mu_F^2) = \qty(\vb C^T(Q^2,\mu_F^2) \otimes \vb f(\mu_F^2))(x) \label{eq:sigmaFC}
\end{equation}
where now $\mu_F$ has its intended place and the usual perturbative expansion of the coefficient function still holds, i.e.\
\begin{equation}
    \vb C(z,Q^2,\mu_F^2) = \sum_{j=0} \qty(\alpha_s(Q^2))^j \vb C^{(j)}(z,\ln(\mu_F^2/Q^2)) \,. \label{eq:CbarFpQCD}
\end{equation}

However, in order to derive an explicit expression for $\vb C(z,Q^2,\mu_F^2)$ it is instructive to start from \enquote{factorization scale variation scheme B}~\cite{NNPDF:2024dpb}.
In this scheme, we make a different choice and attribute the variation instead to the PDF:
\begin{equation}
    \sigma(x,Q^2,\mu_F^2) = \qty(\vb C^T(Q^2) \otimes \vb f^{SV}(\mu_F^2,\ln(\mu_F^2/Q^2)))(x) \label{eq:sigmaFB}
\end{equation}
Note that \cref{eq:sigmaFB} only uses the central coefficient functions $\vb C(Q^2)$, but requires the use of a special PDF $\vb f^{SV}$.
In a PDF fit, where full control over the PDF is required any way and partonic matrix elements (coefficient functions) come from a variety of places, this scheme can be actually preferable.

In order to define $\vb f^{SV}$ we start by observing, that we can write \cref{eq:LOPDFexp} also as a convolution with a factorization scale operator $\vb K$
\begin{equation}
    \vb f(\xi,\mu_F^2) = \qty(\vb K(\mu_F^2 \leftarrow \mu_{F,0}^2) \otimes \vb f(\mu_{F,0}))(\xi)
\end{equation}
where $\vb K$ admits a perturbative expansion
\begin{equation}
    \vb K(y,\mu_F^2 \leftarrow \mu_{F,0}^2) = \sum_{j=0} \qty(\alpha_s(\mu_{F,0}^2))^j \vb K^{(j)}(y,\ln(\mu_F^2/\mu_{F,0}^2))
\end{equation}
and is given up to NLO accuracy by
\begin{equation}
    \vb K(y,\mu_F^2 \leftarrow \mu_{F,0}^2) = \mathbbm{1}\delta(1-y) + \alpha_s(\mu_{F,0}^2) \ln(\mu_F^2/\mu_{F,0}^2) \vb P^{(0)}(y) + \ldots \label{eq:NLOK}
\end{equation}
Here, $\mathbbm 1$ refers to an identity operation in flavour space and $\delta(1-y)$ is the identity in the function convolution space as $\vb K$ is acting on both.

Note that $\vb K$ is a fixed order equivalent of the EKO $\vb E$, but the two are fundamentally different: the latter is a true solution to DGLAP, which must resum all necessary terms, but the former is only an approximation for a small amount of evolution.
Specifically, $\vb K$ only is meaningful when we consider scale variations and in particular we use the interplay between $\vb K$ and $\vb E$ to generate the missing higher order terms we are looking for, because we get
\begin{equation}
    \vb f(\xi,\mu_1^2) = \qty(\vb K(\mu_1^2 \leftarrow \mu_2^2) \otimes \vb E(\mu_2^2 \leftarrow \mu_1^2) \otimes \vb f(\mu_1^2) )(\xi) + \ldots
\end{equation}
where $\ldots$ denotes the missing higher order terms.
Inserting the equation back into \cref{eq:fact3} with $(\mu_1,\mu_2)\to(Q,\mu_F)$ we obtain the definition of our sought-after special PDF
\begin{equation}
    \vb f^{SV}(\xi,\mu_F^2,\ln(\mu_F^2/Q^2)) = \qty(\vb K(Q^2 \leftarrow \mu_F^2)) \otimes \vb f(\mu_F^2))(\xi) \label{eq:fSV}
\end{equation}
where we apply \cref{eq:EKO} for the PDF.
We find $\vb f^{SV}(\xi,\mu_F^2,\ln(\mu_F^2/Q^2)) = \vb f(\xi,Q^2) + \ldots$ as we want to, because then \cref{eq:fact3} and \cref{eq:sigmaFB} differ by higher order terms.

We can now return to the definition of scheme C: we insert \cref{eq:fSV} into \cref{eq:sigmaFB} and obtain
\begin{align}
    \sigma(x,Q^2,\mu_F^2) &= \qty[\vb C^T(Q^2) \otimes \qty(\vb K(Q^2 \leftarrow \mu_F^2) \otimes \vb f^{SV}(\mu_F^2))](x)\\
     &= \qty[\qty(\vb C^T(Q^2) \otimes \vb K(Q^2 \leftarrow \mu_F^2)) \otimes \vb f^{SV}(\mu_F^2)](x) \label{eq:sigmaFCdef}
\end{align}
where we use the associative property of the convolution.
However, we can now re-expand terms in a different order.
First, it is convenient to use the perturbative expansion of the strong coupling to rewrite $\vb K$ in powers of $\alpha_s(Q^2)$ (as opposed to $\alpha_s(\mu_F^2)$, \cref{eq:NLOK}):
\begin{equation}
    \vb K'(y,Q^2 \leftarrow \mu_F^2) = \sum_{j=0} \qty(\alpha_s(Q^2))^j \vb {K'}^{(j)}(y,\ln(\mu_F^2/Q^2))
\end{equation}
with
\begin{equation}
    \vb K'(y,Q^2 \leftarrow \mu_F^2) = \left(\vb K(Q^2 \leftarrow \mu_F^2)\otimes\left[\mathbbm{1} + \order{\alpha_s(Q^2)}\right]\right)(y)
\end{equation}
i.e.\ $\vb K'$ and $\vb K$ differ by higher order terms.
Up to NLO accuracy we find from \cref{eq:NLOK}
\begin{equation}
    \vb K'(y,Q^2 \leftarrow \mu_F^2) = \mathbbm{1}\delta(1-y) - \alpha_s(Q^2) \ln(\mu_F^2/Q^2) \vb P^{(0)}(y) + \ldots \label{eq:NLOKp}
\end{equation}

Second, we identify $\vb C(z,Q^2,\mu_F^2)$ from \cref{eq:sigmaFC} as
\begin{equation}
    \vb C^T(z,Q^2,\mu_F^2) = \qty(\vb C^T(Q^2) \otimes \vb K'(Q^2 \leftarrow \mu_F^2))(z)
\end{equation}
but which is yet another reorganization of the perturbative orders since it turns the product of sums in \cref{eq:sigmaFCdef} into a single sum, \cref{eq:CbarFpQCD}.
Let us see this in practice.

As before, we start from LO accuracy and from \cref{eq:NLOKp} we find immediately
\begin{equation}
    \vb C^{(0)}(z,\ln(\mu_F^2/Q^2)) = \vb C^{(0)}(z), \label{eq:CbarFLO}
\end{equation}
i.e., also here scale variations do not alter the LO coefficient function.
However, unlike in the case for renormalization scale variations, factorization scale variations have always an impact starting from LO accuracy, because PDFs are present per-se in the factorization formula, \cref{eq:fact1}.
Specifically, in any actual calculation with $\mu_F\neq Q$ also $\vb f(\mu_F^2)$ and $\vb f(Q^2)$ are different: they differ by an amount which is beyond our fixed-order framework and if that difference is \enquote{small} depends on the actual values of the PDF of the respective scales.
However, with that we achieve the main purpose of this game: we generate some higher order terms, which we can then use to estimate MHOUs.
This is an intentional copy from \cref{sec:rensv}.

Starting from NLO the matching becomes non-trivial and, e.g., at this order we find
\begin{equation}
    \vb C^{(1),T}(z,\ln(\mu_F^2/Q^2)) = \vb C^{(1),T}(z) -  \ln(\mu_F^2/Q^2) \qty(\vb C^{(0),T} \otimes \vb P^{(0)})(z)\,. \label{eq:CbarFNLO}
\end{equation}
Always remember that for PDF operations, such as acting with the matrix of splitting functions $\vb P(y,\mu_F^2)$, non-commutativity is crucial, i.e., the flavor index dictated by the left-hand-side of \cref{eq:CbarFNLO} is matched by the second term on the right-hand-side by a vector-matrix multiplication (from the left).
Note that starting from NNLO also explicit coefficients of the beta function start to appear, since the logarithm $\ln(\mu_F^2/Q^2)$ is coming directly from the running of the strong coupling, \cref{eq:LOalphasresum}.
In other words: PDF evolution resums logarithms through the running of the strong coupling.

In the following we assume scheme C as our default choice, thus \cref{box:svren} holds also for factorization scale variations and we can improve \cref{eq:fact3} with \cref{eq:sigmaFC}.
The case of scheme B\footnote{scheme A is doing yet something different - see Ref.~\cite{NNPDF:2024dpb}} is slightly more complicated, as explained above, but straightforward to obtain.

\subsection{Combined variation}
We recall, the renormalization and factorization scales are two independent scales, related to two different kind of physics.
The former captures ultra-violet and the latter collinear divergencies.
While we discuss them one at a time above, in practice we have to consider them simultaneously.
In order to do so, we must first consider factorization scale variation, which yields \cref{eq:sigmaFC},
\begin{equation}
    \sigma(x,Q^2,\mu_F^2,\mu_R^2=Q^2) = \qty(\vb C^T(Q^2,\mu_F^2,\mu_R^2=Q^2) \otimes \vb f(\mu_F^2))(x)
\end{equation}
but now we make the renormalization scale dependence explicit and $\vb C(Q^2,\mu_F^2,\mu_R^2=Q^2)$ corresponds to \cref{eq:CbarFpQCD}.
Then in the second step, we apply the renormalization scale variation onto $\vb C(Q^2,\mu_F^2,\mu_R^2=Q^2)$, which still depend on $\alpha_s(Q^2)$, and get
\begin{equation}
    \sigma(x,Q^2,\mu_F^2,\mu_R^2) = \qty(\vb C^T(Q^2,\mu_F^2,\mu_R^2) \otimes \vb f(\mu_F^2))(x)\,. \label{eq:sigmaFR}
\end{equation}
We can make the dependence on the various scales in \cref{eq:sigmaFR} more explicit by rewriting it as
\begin{equation}
    \sigma(x,Q^2,\mu_F^2,\mu_R^2) = \qty(\vb C^T(\alpha_s(\mu_R^2),\ln(\mu_F^2/Q^2),\ln(\mu_R^2/Q^2)) \otimes \vb f(\mu_F^2))(x) \label{eq:sigmaFRln}
\end{equation}
where, again, finally $\mu_F$ and $\mu_R$ fulfill their dedicated role.
Note that in \cref{eq:sigmaFRln} two additional scales, $\mu_{F,0}$ and $\mu_{R,0}$ are left implicit and those eventually guarantee that it is a dimensionless equation.

Let us see this in practice and remember that in order to see renormalization scale logarithms we need to play at NNLO.
We find
\begin{align}
    &\vb C(z,\alpha_s(\mu_R^2),\ln(\mu_F^2/Q^2),\ln(\mu_R^2/Q^2)) \nonumber\\
    &= \vb C^{(0)}(z) \nonumber\\
     &\hspace{10pt} + \alpha_s(\mu_R^2) \left[\vb C^{(1)}(z) + \vb C^{(1),F}(z)\ln(\mu_F^2/Q^2) \right] \nonumber\\
     &\hspace{10pt} + \left(\alpha_s(\mu_R^2)\right)^2 \left[\vb C^{(2)}(z) + \vb C^{(2),F}(z)\ln(\mu_F^2/Q^2) + \vb C^{(2),R}(z)\ln(\mu_R^2/Q^2) \right.\nonumber\\
     &\hspace{70pt} \left. \vb C^{(2),FF}(z)\ln^2(\mu_F^2/Q^2) + \vb C^{(2),FR}(z)\ln(\mu_F^2/Q^2)\ln(\mu_R^2/Q^2) \right] + \ldots
\end{align}
An explicit expression for $\vb C^{(1),F}$ is given in \cref{eq:CbarFNLO} and for $\vb C^{(2),R}$ in \cref{eq:CbarRimpl}.
We see that the number of terms per perturbative order quickly grows as the respective algorithms collect more of the full behavior.
% mention cross term? C^2F = C^1 P^0 + C^0 P^1
The appearance of $\vb C^{(2),FR}$ also demonstrate how the two variations become intertwined.

% 7 vs 9 pnt?
% correlations?
% covariance matrix?

\subsection{Discussion}
\label{sec:svdiscussion}
The renormalization and factorization scale are remnants of the necessary regularization of UV and collinear divergencies.
Although, scale variations are a genuine pQCD property they have some features, which questions their usefulness for estimating MHOUs.

When introducing the scales, we are required to set them to \enquote{a typical scale of the process}, which makes them inherently arbitrary from the start before doing any variation.
In fully inclusive DIS there is a single scale available, the virtuality $Q^2$, and thus the common choice is $\mu_F^2 = Q^2 = \mu_R^2$, but any multiplicative there of could work just as well\footnote{For example CT18X~\cite{Hou:2019efy} makes a different choice.}.
If we want to use scale variations to estimate MHOU, we need to make a further arbitrary choice about which range we want to use for the respective scales and if we want to correlate them.
As we see in \cref{box:svren} the scale-varied coefficient functions are always a linear combination of the existing ones, i.e.\ they can not introduce new channels (new PDF combinations).
However, it is often straightforward to show that a new channel should appear although its size is unknown and scale variations are unable to predict this.
An example for such a scenario in fully inclusive DIS can be seen at NLO: starting from NLO the gluon can participate in the scattering, but the LO only contains quark PDFs.
In other cases, we know that higher orders must contain certain kinematic logs, e.g. from particles radiating at small and/or large transverse momentum or in the soft limit and in fully inclusive DIS the latter is the case\footnote{More mathematically speaking: soft gluon resummation is a double logarithmic resummation $\tilde c_q^{(j)} \sim \alpha_s^j \ln^{2j}(N)$ for $N\to\infty$ in Mellin space, \cref{eq:Mellinf}. Double logarithmic structures can not be predicted by scale variations.}.
Also those corrections can (in many cases) not be predicted by scale variations.

Scale variations also provide no statistical interpretation, which is in stark contrast to experimental uncertainties, where we usually assume Gaussian uncertainties and thus the provided error has a clear interpretation.
However, strictly speaking even there this only applies to statistical errors but not to systematic errors and the question which of the two dominates depends very much on the specific measurement.

Despite all these (potential) problems, scale variations have a solid foundation in QFT and can be applied (straightforwardly) to any pQCD process, which makes them an easy tool to estiate MHOU.
In order to make a faithful statement, we can then simply say: when we compute this process with this specific choice of scale, we obtain this number; if we vary that scale in this range, we obtain this range of numbers.

\subsection{Implementation and flavor space}
\label{sec:svimpl}
Let us return to more practical consequences.
As we see above, renormalization scale variations are just a scalar operation, but factorization scale variations are more complicated and it is worth spelling out their explicit construction to see what is actually happening.

The factorization scale variation is directly related to the PDFs themselves and, in particular, eventually, they derive from \cref{eq:DGLAP}.
However, the splitting functions $\vb P$ are encoding how partons couple among each other, which is through the gluon\footnote{for quark-photon interaction see Ref.~\cite{NNPDF:2024djq}} of course.
This is in contrast to DIS, where instead the coefficient functions are encoding how partons couple to the electro-weak vector boson, which is completely different, see \cref{box:particles}.

At LO accuracy the problem does not appear yet, because there are no scale-varied coefficient functions, see \cref{eq:CbarFLO}, but starting from NLO accuracy we need to worry.
In particular, we know that the gluon couples the same to all quarks, thus, if we assume four flavors for the moment (see \cref{sec:hq}) and combine them in the following way~\cite{NNPDF:2024djq}\footnote{for the more general case see Ref.~\cite{NNPDF:2024djq}},
\begin{align}
    f_{\Sigma_\Delta}(x,Q^2) &= f_u(x,Q^2) + f_{\bar u}(x,Q^2) + f_c(x,Q^2) + f_{\bar c}(x,Q^2)\nonumber\\
    & \hspace{10pt} - f_d(x,Q^2) - f_{\bar d}(x,Q^2) - f_s(x,Q^2) - f_{\bar s}(x,Q^2)  \label{eq:SigmaDelta}
\end{align}
we know that this combination does not interact with the gluon.
In order to see more clearly what happens we need to go back to the vector notation from \cref{eq:fact3}.
We repeat: we denote objects, which have a non-trivial dependence on the parton flavors, with bold font.
This applies to vectors in flavor space, e.g.\ coefficient functions $C_j \to \vb C$ or PDFs $f_j \to \vb f$, but also to matrices, e.g.\ splitting functions $P_{jk} \to \vb P$ or the factorization scale operator $K_{jl}\to \vb K$.
By introducing the vector notation we hide any reference to a given basis in the flavor space, which now becomes relevant (see also \cref{sec:hq}).

Let us be more formal.
We define the flavor space $\mathcal F$ as the vector space spanned by the gluon and all quark flavors.
We consider the naive flavor basis as our canonical basis and write
\begin{equation}
    \mathcal F = \mathrm{span}(g, u, \bar u, d, \bar d, s, \bar s, c, \bar c, b, \bar b, t, \bar t)\,. \label{eq:flspace}
\end{equation}
We have a 13 dimensional vector space, $\dim{\mathcal F} = 13$\footnote{one can add the photon and make it 14 dimensional~\cite{NNPDF:2024djq}}, consisting of the gluon, six quarks, and six anti-quarks.
Our bold vectors are an element in that space, e.g.\ $\vb C \in \mathcal F$, or more plainly,
\begin{equation}
    \vb C^T \sim (C_g, C_u, C_{\bar u}, C_d, C_{\bar d}, C_s, C_{\bar s}, C_c, C_{\bar c}, C_b, C_{\bar b}, C_t, C_{\bar t})
\end{equation}
and, of course, any other basis works just as well.
The same applies also to the PDF $\vb f$, which is the other vector in \cref{eq:fact3}, and any operator, e.g.\ splitting functions $\vb P$, just lives in the product space, $\vb P \in \mathcal F \otimes \mathcal F$.
The flavor basis is handy for computing LO and NLO DIS coefficient functions, i.e.\ we consider each quark individually and we can find easily \cref{eq:LOC,eq:LOxs}.

For the discussion in \cref{sec:DGLAP} and in particular for dealing with splitting functions, $\vb P$, a different basis is more convenient: the evolution basis.
The two choices are both orthogonal bases, i.e.\ they are simply related by a rotation\footnote{actually, it is a rotation and a scaling, i.e.\ the evolution basis is not orthonormal, which may cause some trouble} in flavor space.
Specifically, $\vb P$ has a much simpler representation if one of the basis vectors is the flavor singlet
\begin{align}
    f_\Sigma(x,Q^2) &= f_u(x,Q^2) + f_{\bar u}(x,Q^2) + f_c(x,Q^2) + f_{\bar c}(x,Q^2)\nonumber\\
    & \hspace{10pt} + f_d(x,Q^2) + f_{\bar d}(x,Q^2) + f_s(x,Q^2) + f_{\bar s}(x,Q^2) \label{eq:Singlet}
\end{align}
and all other basis vectors can be chosen such that they do not couple to the gluon, e.g. \cref{eq:SigmaDelta}.

Let us see this in practice for LO photon DIS: we start from \cref{eq:LOC}, which is written in flavor basis, i.e.\ for each given quark flavor and the gluon.
Inserting \cref{eq:LOC} into \cref{eq:fact1} yields \cref{eq:LOxs} and we find explicitly
\begin{align}
    \sigma(x,Q^2) &= e_u^2\qty(f_u(x,Q^2) + f_{\bar u}(x,Q^2) + f_c(x,Q^2) + f_{\bar c}(x,Q^2)) \nonumber\\
    & \hspace{10pt} + e_d^2\qty(f_d(x,Q^2) + f_{\bar d}(x,Q^2) + f_s(x,Q^2) + f_{\bar s}(x,Q^2))\,.
\end{align}
Using \cref{eq:Singlet,eq:SigmaDelta} we can rewrite this in evolution basis
\begin{equation}
    \sigma(x,Q^2) &= \frac{e_u^2 + e_d^2} 2 f_\Sigma(x,Q^2) + \frac{e_u^2 - e_d^2} 2 f_{\Sigma_\Delta}(x,Q^2)
\end{equation}
or equivalently
\begin{equation}
    C_\Sigma^{(0)}(z) = \frac{e_u^2 + e_d^2} 2 \delta(1-z),\quad C_{\Sigma_\Delta}^{(0)}(z) = \frac{e_u^2 - e_d^2} 2 \delta(1-z), \quad C_j(z) = 0 \,\forall j\neq\{\Sigma,\Sigma_\Delta\} \label{eq:LOCev}
\end{equation}
where the parton index $j$ in \cref{eq:fact1} now also runs over the evolution basis.
We stress that \cref{eq:LOC,eq:LOCev} are two equivalent representation of the coefficient function $\vb C^{(0)}$ using two different bases.

Moving to NLO, we have the same structure in the quark sector, \cref{eq:NLOCq}, and we encounter for the first time the gluon channel, \cref{eq:NLOCg}.
Thus, when we want to execute \cref{eq:CbarFNLO}, we need to consider three directions in flavor space: the gluon, the singlet $f_\Sigma$ and $f_{\Sigma_\Delta}$, \cref{eq:SigmaDelta}.
The preferred basis for $\vb P$ is manifest by the following statements,
\begin{equation}
    \mathrm P_{\Sigma \Sigma_\Delta}(y) = \mathrm P_{g \Sigma_\Delta}(y) = \mathrm P_{\Sigma_\Delta \Sigma}(y) = \mathrm P_{\Sigma_\Delta g}(y) = 0
\end{equation}
which do not occur in flavor basis.
Eventually, \cref{eq:CbarFNLO} becomes explicitly
\begin{align}
    C^{(1)}_{\Sigma_\Delta}(z,\ln(\mu_F^2/Q^2)) &= C^{(1)}_{\Sigma_\Delta}(z) - \ln(\mu_F^2/Q^2) \qty(C^{(0)}_{\Sigma_\Delta} \otimes \mathrm P_{\Sigma_\Delta \Sigma_\Delta}^{(0)})(z)\\
    C^{(1)}_{\Sigma}(z,\ln(\mu_F^2/Q^2)) &= C^{(1)}_{\Sigma}(z) - \ln(\mu_F^2/Q^2) \qty(C^{(0)}_{\Sigma} \otimes \mathrm P_{\Sigma \Sigma}^{(0)})(z)\\
    C^{(1)}_{g}(z,\ln(\mu_F^2/Q^2)) &= C^{(1)}_{g}(z) - \ln(\mu_F^2/Q^2) \qty(C^{(0)}_{\Sigma} \otimes \mathrm P_{\Sigma g}^{(0)})(z) \label{eq:NLOCbarFg}
\end{align}
where the required splitting functions can be found in the literature~\cite{Leader:2011gpt,Leader:1996hm,Peskin:1995ev}.

Actually, also LO splitting functions $\vb P^{(0)}$ obey symmetry relations, in particular all quarks couple identically to the gluon and it is not possible (yet) to change the quark flavor.
This implies $\mathrm P_{\Sigma_\Delta \Sigma_\Delta}^{(0)}(y) = \mathrm P_{\Sigma \Sigma}^{(0)}(y) = \mathrm P_{qq}^{(0)}(y)$ and thus \cref{eq:CbarFNLO} can also be executed straightforwardly in flavor space.
However, this symmetry breaks down starting from NLO splitting functions $\vb P^{(1)}$, which would be required for NNLO DIS cross sections.

\subsection{Interplay with previous content}

\begin{itemize}
    \item Renormalization scale variation is a reshuffling of lower order coefficient functions and factorization scale variation adds convolutions between splitting functions and lower order coefficient functions.
        This implies that the mathematical complexity remains the same or in other words: we never encounter new mathematical objects in scale variations; see \cref{sec:nlo}.
    \item Although scale-varied coefficient functions can always be computed a posteriori, see \cref{box:svren}, in practice it usually makes sense to tabulate them into interpolation grids as well, see \cref{sec:grids}.
        These additional coefficient functions can be easily accommodated when we generalize our concept of \enquote{order}: it can not only represent the perturbative order per se, but also additional powers of renormalization or factorization logarithms: $\alpha_s^k(\mu_R^2)\ln^m(\mu_R^2/Q^2)\ln^n(\mu_R^2/Q^2)$.
    \item The necessary projection onto a singlet component is particularly tricky for CC DIS, see \cref{sec:diverse}.
        Recall that the $W^\pm$ boson only couple to specific PDFs and thus if we want to project the coefficient functions into evolution basis we need the full basis (and not just \cref{eq:SigmaDelta,eq:Singlet}).
    \item Note that the coupling structure is always retained, i.e.\ e.g.\ in \cref{eq:NLOCbarFg}
        \begin{equation}
            C^{(1)}_{g}(z) \sim e_u^2 + e_d^2 \sim C^{(1)}_{g}(z,\ln(\mu_F^2/Q^2))\,.
        \end{equation}
        This implies that a given \enquote{channel} in an interpolation grid (\cref{sec:grids}) has a unique coupling, though recall that some channels only appear at high enough perturbative order.
\end{itemize}
