When we compute LO DIS from \cref{fig:LO} we say it is easy to identify the respective coefficient function, \cref{eq:LOC}.
However, what exactly do we mean with the \enquote{$\forall q$}?
Which quarks are we exactly talking about?
This is directly linked to the flavor space to which we hint when using bold font.
However, unlike the problem we discuss in \cref{sec:svimpl} about different bases (flavor basis vs.\ evolution basis), here we are more directly concerned what the flavor space is in the first place.

The question we need to address here is: which quarks exactly can participate in \cref{eq:LOxs,eq:LOC}?
We refer to this number as the number of active quarks $n_f$.
This dependency is completely hidden in \cref{eq:fact1}, but, as we demonstrate in the following, is a major concern for both coefficient functions and PDF.
Note that the gluon is always considered active and contributes to all diagrams always.

The number of flavors $n_f$ is arbitrary per se and there is no absolutely correct answer, since there is no theory argument, which would fix this choice.
However, in practice for a given observable $\sigma(x,Q^2)$ we can consider, which options are phenomenologically reasonable and if some option would yield unstable results.

For the sake of the argument, let's consider a fully inclusive DIS cross section $\sigma(x,Q^2=\SI{25}{\GeV^2})$, so we probe the probe the proton at $\mu_F=Q=\SI{5}{\GeV}$.
We can now consider the different quark masses as a guideline: on the one side the masses of up, down, and strange are significantly below the non-perturbative regime of QCD $m_u,m_d,m_s \ll \LQCD \sim \SI{1}{\GeV}$ and we can safely assume we can find them in the proton.
On the other side the mass of the top is significantly above the probed scale, $m_t \gg Q$, thus it is very unlikely to find it in the proton and we can neglect it.
We can shut down such contributions by setting $f_t(\xi, Q^2) = 0 = f_{\bar t}(\xi, Q^2)$ and this way the top quark does not contribute to \cref{eq:fact1}.
In addition, we can also define $C_t(z, Q^2) = 0 = C_{\bar t}(z, Q^2)$ to explicitly say that we don't let the top contribute.

Now, we consider the two remaining quarks, charm and bottom, for which maybe there is no clear answer.
First, for the charm quark we have $m_c \sim \SI{1.5}{\GeV}$ and we can assume reasonably that it can contribute to this cross section.
On the other side, for the bottom quark we have $m_b \sim \SI{4.5}{\GeV}$ and maybe we can both allow or deny it.
The specific choice on which quarks we allow to participate and in which way they do so is referred to as flavor number scheme (FNS).

\subsection{ZM-VFNS}

One very popular choice is the Zero-Mass Variable Flavor Number Scheme (ZM-VFNS), which is a telling name and which we have silently adopted in the previous parts.
Formally, we can define it in the following way:
first, whenever the probed scale $Q$ crosses a quark mass that quark becomes active;
second; in coefficient functions all active quarks are considered massless and all non-active quarks are considered infinite massive.
The infinite mass ensures $f_H(\xi, Q^2) = 0 = f_{\bar H}(\xi, Q^2)$ and $C_H(z, Q^2) = 0 = C_{\bar H}(z, Q^2)$ for all non-active quarks $H$ and the zero mass ensures that all formulas in \cref{sec:nlo} hold.
If we denote the new dependency on the number of active flavors $n_f$ by a superscript $(n_f)$ we can define the ZM-VFNS in the following way
\begin{equation}
    \sigma^{\text{ZM-VFNS}}(x,Q^2) = \left\{ \begin{array}{ll}
        \sigma^\mathrm{(3)}(x,Q^2) &\text{if}~ Q^2 < m_c^2\\
        \sigma^\mathrm{(4)}(x,Q^2) &\text{if}~ m_c^2 \leq Q^2 < m_b^2\\
        \sigma^\mathrm{(5)}(x,Q^2) &\text{if}~ m_b^2 \leq Q^2 < m_t^2\\
        \sigma^\mathrm{(6)}(x,Q^2) &\text{if}~ Q^2 \geq m_t^2
    \end{array} \right. \label{eq:zmvfns}
\end{equation}
where
\begin{equation}
    \sigma^{(n_f)}(x,Q^2) = \left(\vb C^{T,(n_f)}(Q^2) \otimes \vb f^{(n_f)}(Q^2)\right)(x) \label{eq:factnf}
\end{equation}
i.e.\ each contribution has its own factorization formula and we have, e.g.,
\begin{equation}
    \begin{array}{l}
        C_H^{(3)}(z, Q^2) = 0 = C_{\bar H}^{(3)}(z, Q^2)\\
        f_H^{(3)}(\xi, Q^2) = 0 = f_{\bar H}^{(3)}(\xi, Q^2)
    \end{array}
    \quad H\in\{c,\bar c, b, \bar b, t, \bar t\}
\end{equation}
and similar for the others.
Specifically, we can improve \cref{eq:LOC} by writing
\begin{align}
    C_q^{(0),(3)}(z) &= e_q^2 \delta(1-z) & q\in\{c,\bar c, b, \bar b, t, \bar t\}\\
    C_H^{(0),(3)}(z) &= 0 & H\in\{c,\bar c, b, \bar b, t, \bar t\}\\
    C_g^{(0),(3)}(z) &= 0
\end{align}
and we finally give full details on the available flavor space $\mathcal F$.

Note that it does not make sense to consider less then three quarks, since $m_u,m_d,m_s \ll \LQCD \sim \SI{1}{\GeV}$ and pQCD only works for $Q > \LQCD$.
All quarks are considered with their actual mass for the decision if they are in or out, \cref{eq:zmvfns}, but then after that their mass is discarded when computing $\vb C^{(n_f)}(z,Q^2)$.
Thus, the VFNS indicates that the number of active quarks $n_f$ depends on the probed scale $Q$, i.e.\ it is variable, and the ZM explains how to compute diagrams.
However, once we have an actual scale in hand, $n_f$ is also fixed.

\begin{conclusionbox}{ZM-VFNS}
    In the ZM-VFNS
    \begin{itemize}
        \item the number of active quarks $n_f$ depends on the probed scale $Q^2$
        \item contain the diagrams to compute coefficient functions only massless quarks
    \end{itemize}
\end{conclusionbox}

\subsection{FFNS}
\label{sec:ffns}

For the number of active quarks we can make another simple choice: fix $n_f$ once and forever - the Fixed Flavor Number Scheme (FFNS).
Here, the probed scale $Q$ does not matter, but we use the same coefficient functions for any scale.
Actually, saying FFNS is not sufficient, we still have some choices and the most obvious is $n_f$.

However, we can also improve with respect to other parts: while it is significantly easier to compute diagrams with only massless quarks, we can compute them also with massive quarks.
For simplicity we assume in the following we have exactly one\footnote{the case of two massive quarks is e.g.\ discussed in Ref.~\cite{Barontini:2024xgu}} massive quark with mass $m^2$.
Moreover, while we keep the notation general you can always consider as a concrete example $n_f=3$ and thus $m^2 = m_c^2$.
We recall two important features of the propagator of a massive quark,
\begin{equation}
    D_q(p) \sim \frac{p_\mu\gamma^\mu + m\mathbbm{1}}{p^2 - m^2}\,; \label{eq:quarkprop}
\end{equation}
first, the mass appears explicitly in the numerator, which makes computing Dirac traces significantly more lengthy, and, second, the mass appears in the denominator, which shields the propagator from a collinear pole.
When we consider a finite mass we eventually have three different scales in our diagrams: the total energy of the colliding partons $\hat s$, the photon virtuality $Q^2$, and the quark mass $m^2$.
This means that unlike the massless case discussed so far, the coefficient functions now depend on two scales, for example the partonic momentum fraction $z = Q^2/(\hat s + Q^2)$ and $\xi_q = Q^2 / m^2$ or any other bijective combination\footnote{For example, for NC DIS on can show~\cite{Hekhorn:2019nlf} that $\chi = \frac{1-\sqrt{1-4m^2/s}}{1+\sqrt{1-4m^2/s}}$ and $\chi_q = \frac{\sqrt{1+4m^2/Q^2}-1}{\sqrt{1+4m^2/Q^2}+1}$ are good combinations.}.
This in turn implies that the available mathematical function space is much bigger, which makes the computation of these coefficient functions $\vb C(z,\xi_q,Q^2)$ significantly more complex.

However, we focus here on the new dependency on $\xi_q$, which captures the new features.
First, we consider the case $Q^2 \gg m^2$ or $\xi_q \to \infty$ where the denominator of \cref{eq:quarkprop} plays the important role.
Indeed, since it is shielding the propagator from a collinear divergency, we encounter some signals thereof when we put $m^2 \to 0$.
Specifically, we can rewrite the coefficient functions in this limit,
\begin{equation}
    \lim_{Q^2/m^2\to\infty}\vb C^{(n_f),T}(Q^2,m^2) = \vb C^{(n_f+1),T}(Q^2) \vb A^{(n_f+1)}(Q^2,m^2) \label{eq:Cmatching}
\end{equation}
i.e.\ we can connect the coefficient functions using two neighboring schemes and a new, universal operator $\vb A$, which admits a perturbative series
\begin{equation}
    \vb A^{(n_f+1)}(Q^2,m^2) = \sum_{j=0} \left(\alpha_s(Q^2)\right)^j \vb A^{(j),(n_f+1)}(\ln(Q^2/m^2))\,.
\end{equation}
We discuss more details of this new operator in a moment, but the important thing to stress here is the universality.
This universality derives from the universality of PDFs, which makes the operator closely connected to collinear splitting functions as we expect.
Moreover, \cref{eq:Cmatching} puts strong constraints on the computation of any coefficient function\footnote{or any partonic matrix elements as a similar equations hold, e.g., in hadron-hadron collisions} once the universal operator $\vb A$ is known at the requested accuracy.
Note that the coefficient functions in \cref{eq:Cmatching} depend on different sets of variables, since we consider the \enquote{+1} quark massless in the $(n_f+1)$ scheme.
Thus, as expected, the full mass dependence on the right-hand-side of \cref{eq:Cmatching} is carried by the universal operator $\vb A$ and it is a pure, actual polynomial, dependency on $\ln(Q^2/m^2)$.
So, the remnant of the collinear divergency for a massive quark is a logarithm $\ln(Q^2/m^2)$ as we may have guessed from the beginning.

Next, we consider the case $Q^2 \sim m^2$ where the nominator of \cref{eq:quarkprop} plays the important role.
While we conclude above that the FFNS coefficient functions contain logarithms $\ln(Q^2/m^2)$ they also naturally contain terms which are relatively suppressed to them.
Specifically, if we expand the FFNS coefficient function around $Q^2 \sim m^2$ we obtain
\begin{equation}
    \vb C^{(n_f)}(Q^2,m^2) = \vb C_{thr,0}^{(n_f)} + \vb C_{thr,1}^{(n_f)} \left(\frac{Q^2}{m^2}\right) + \vb C_{thr,2}^{(n_f)} \left(\frac{Q^2}{m^2}\right)^2 + \ldots \label{eq:Cpower}
\end{equation}
with some coefficients $\vb C_{thr,k}^{(n_f)}$.
Note that the equation is to be understood as a Taylor expansion at the requested point as in practice the actual dependency on $\xi_q$ is very intricate\footnote{for example via $\chi_q$}.
However, it is clear that in the region $Q^2 \sim m^2$ these terms may not be small and thus neglecting such contributions may yield wrong results.
That is the precisely the advantage of FFNS over ZM-VFNS: while in the latter we explicitly deny any massive quark in the diagrams, the former allows them to be included in the sum over diagrams.

\begin{conclusionbox}{FFNS}
    In the FFNS
    \begin{itemize}
        \item massive quarks are allowed in the computation of diagrams for coefficient functions
        \item we counter universal logarithms $\ln(Q^2/m^2)$ for $Q^2\to m^2$ due to collinear divergencies
    \end{itemize}
\end{conclusionbox}

But if the FFNS calculation is actually better than ZM-VFNS, why don't we always use the former?
Before answering the question, we need to return to the new operator $\vb A$.

\subsection{Matching schemes}
\label{sec:matching}

The number of active quarks is not only relevant for coefficient functions, but, in fact, for the whole pQCD program and in particular for the strong coupling $\alpha_s$ and PDFs $\vb f$.
As we see from \cref{eq:factnf} also PDFs depend on the number of flavors, e.g.\ $\vb f^{(3)}(\xi,\mu_F^2)$, and we can improve \cref{eq:CpQCD} with
\begin{equation}
    \vb C^{(n_f)}(z,Q^2,m^2) = \sum_{k=0} \left(\alpha_s^{(n_f)}(Q^2)\right)^k \vb C^{(k),(n_f)}(z,\xi_q)
\end{equation}
where we now also explicitly denote the flavor dependence of the strong coupling.
Actually, from \cref{eq:LObeta} we already known that the beta coefficients depend explicitly on $n_f$ and thus $\alpha_s$ must depend on it as well.
The same applies to PDFs since also splitting functions carry an explicit $n_f$ dependence and all appearances above, indeed, correspond to $\vb P^{(n_f)}$.

The question is: how are those different schemes, e.g.\ $\alpha_s^{(3)}$ and $\alpha_s^{(4)}$, connected with each other?
For coefficient functions the difference originates from the different diagrams which are included into the calculation of the coefficient functions, $\vb C^{(3)}$ and $\vb C^{(4)}$, but what about the strong coupling $\alpha_s$ and the PDFs $\vb f$?
In order to answer this question it is important to return to the basic principles: we know that only cross sections $\sigma$ are physical objects for which we can derive physical properties, e.g.\ that they must be positive.
In contrast, the strong coupling $\alpha_s$, PDFs $\vb f$, and coefficient functions $\vb C$ are not physical objects, which can not be measured directly in an experiment and which only are defined within our framework of pQCD.
The concept of having different number of active flavors $n_f$ is a theoretical idea, which we employ to make a consistent approximation in our calculation, but is irrelevant to nature.
In pQCD we can still derive certain rules for our relevant objects in order to obtain a consistent theory, which we can then use to make predictions.

The important physical properties, which we need here is consistency and perturbative equivalence.
Specifically, we require that the cross section in two different scheme are perturbatively equivalent, i.e.\
\begin{equation}
    \sigma^{(n_f)}(x,Q^2) = \sigma^{(n_f+1)}(x,Q^2)\left[1 + \order{\alpha_s^{(n_f+1)}(Q^2)}\right]\,, \label{eq:sigmamatching}
\end{equation}
where the two cross section are consistently computed in their respective flavor number scheme.
In particular, they use their own coefficient functions, their own strong coupling, and their own PDFs.
However, since the coefficient functions, the beta coefficients, and the splitting functions are computed from the respective relevant diagrams this makes the condition quite restrictive.
Moreover, if we recall \cref{sec:resum} we know that both, $\alpha_s$ and $\vb f$, perform a resummation, so \cref{eq:sigmamatching} is to be understood in a logarithmic sense and thus, in practice, it is convenient to consider \cref{eq:sigmamatching} in the limit $Q^2 \to \infty$.

One can show~\cite{Barontini:2024xgu} that the connection between two different schemes can be done by a universal matching procedure for the strong coupling and the PDFs.
Specifically, for the strong coupling we find
\begin{equation}
    \alpha_s^{(n_f+1)}(\mu_R^2) = \zeta^{(n_f+1)}(\mu_R^2, m^2)\alpha_s^{(n_f)}(\mu_R^2) \label{eq:alphasmatching}
\end{equation}
with a universal matching operator $\zeta$, which admits a perturbative series and has a polynomial dependence on $\ln(\mu_R^2/m^2)$.
Analogously, for the PDFs we find
\begin{equation}
    \vb f^{(n_f+1)}(\xi, \mu_F^2) = \left(\vb A^{(n_f+1)}(\mu_F^2, m^2) \otimes \vb f^{(n_f)}(\mu_F^2)\right)(\xi) \label{eq:pdfmatching}
\end{equation}
with a universal matching operator $\vb A$, which is also used in \cref{eq:Cmatching}.
The scheme change, \cref{eq:alphasmatching} and \cref{eq:pdfmatching}, can be done at any scale, but, following \cref{eq:zmvfns}, is conventionally done at the mass of the heavy quark, $\mu_R^2 = m^2 = \mu_F^2$.

Let's see this in practice: consider a cross section $\sigma(x,Q^2)$ with $Q^2 > m^2$.
As we say above the number of active quarks is a free choice, we can compute the cross section either in the $n_f$ scheme, \cref{eq:factnf}, or in the $(n_f+1)$ scheme,
\begin{equation}
    \sigma^{(n_f+1)}(x,Q^2) = \left(\vb C^{T,(n_f+1)}(Q^2) \otimes \vb f^{(n_f+1)}(Q^2)\right)(x)\,. \label{eq:sigmaup}
\end{equation}
Inserting \cref{eq:pdfmatching} into \cref{eq:sigmaup} we obtain
\begin{equation}
    \sigma^{(n_f+1)}(x,Q^2) = \left(\vb C^{T,(n_f+1)}(Q^2) \otimes \vb A^{(n_f+1)}(Q^2,m^2) \otimes \vb f^{(n_f)}(Q^2)\right)(x) \label{eq:sigmaupmatched}
\end{equation}
and if \cref{eq:Cmatching} holds, the two expressions, \cref{eq:factnf} and \cref{eq:sigmaup}, are actually perturbatively equivalent.
Recall that \cref{eq:Cmatching} only holds in the $Q^2 \gg m^2$ limit and so in practice for finite $Q^2$ the two expression are only perturbatively equivalent.

\Cref{eq:alphasmatching,eq:pdfmatching} imply that the two quantities are not continuous across the matching, but they differ by the application of the matching operator.
Actually, at low enough perturbative order the matching operator, $\zeta$ and $\vb A$, are trivial (e.g.\ $\zeta(\mu_R^2,m^2) = 1+\order{\alpha_s(\mu_R^2)}$) and the discontinuity is a higher-order effect.
The strong coupling, the PDFs, and the coefficient function, who are on their own all discontinuous, conspire together in such a way that the cross section is continuous at the requested accuracy, \cref{eq:sigmamatching}.
This maps directly to the statement from \cref{sec:basics} that the cross section is a measurable object, which obviously must be continuous, but the others not.

\subsection{FONLL as an example of a GM-VFNS}

Let's return to the question on why we not always consider the FFNS.
Looking to \cref{eq:sigmaupmatched}, we note that we have matched the PDF at $Q^2$, which is what we have needed there to make the argument of consistency work.
However, we also say that the usual thing instead is to match at the heavy quark mass $m^2$, so let's see how that plays out.
Starting from \cref{eq:sigmaup}, we find
\begin{align}
    &\sigma^{(n_f+1)}(x,Q^2) \nonumber\\
    &= \left(\vb C^{T,(n_f+1)}(Q^2) \otimes \vb f^{(n_f+1)}(Q^2)\right)(x)\\
    &= \left(\vb C^{T,(n_f+1)}(Q^2) \otimes \vb E^{(n_f+1)}(Q^2 \leftarrow m^2) \otimes \vb f^{(n_f+1)}(m^2)\right)(x)\\
    &= \left(\vb C^{T,(n_f+1)}(Q^2) \otimes \vb E^{(n_f+1)}(Q^2 \leftarrow m^2) \otimes \vb A^{(n_f+1)}(m^2,m^2) \otimes \vb f^{(n_f)}(m^2)\right)(x) \label{eq:sigmaup0}
\end{align}
where in the second equation we have inserted the EKO in the $(n_f+1)$ scheme, $\vb E^{(n_f+1)}$, from \cref{eq:EKO} and then in the third equation the matching, \cref{eq:pdfmatching}, which is now in the customary place.
We can massage \cref{eq:factnf} in a similar way and find
\begin{align}
    \sigma^{(n_f)}(x,Q^2) &= \left(\vb C^{T,(n_f)}(Q^2) \otimes \vb f^{(n_f)}(Q^2)\right)(x)\\
    &= \left(\vb C^{T,(n_f)}(Q^2) \otimes \vb E^{(n_f)}(Q^2 \leftarrow m^2) \otimes \vb f^{(n_f)}(m^2)\right)(x) \label{eq:sigma0}
\end{align}
with the EKO now in the $n_f$ scheme, $\vb E^{(n_f)}$.

As we discuss in \cref{sec:resum} the EKO, $\vb E$, is performing a resummation and in this particular case a resummation of the logarithm $\log(Q^2/m^2)$ as can be seen from the arguments in \cref{eq:sigmaup0,eq:sigma0}.
This is true in either scheme, but the amount of logarithms, meaning the prefactor that is resummed along side, is different.
The resummation is directly proportional to the splitting functions, \cref{eq:LOPDFexp}, which is different between the two scheme.
In particular, in the $(n_f)$ scheme we are resumming the collinear logs of $n_f$ light quarks, but in the $(n_f+1)$ scheme we are resumming the collinear logs of $(n_f+1)$ light quarks.
Thus the latter contains effectively more logarithms.

But then how could we find an equivalence between the two schemes in \cref{sec:matching}?
Recall that the equivalence is valid for cross sections, where coefficient functions explicitly enter, \cref{eq:factnf}.
Indeed from \cref{sec:ffns} we know that $\vb C^{(n_f)}(z,Q^2,m^2)$ contains logarithms $\ln(Q^2/m^2)$, which are precisely the ones we are hunting here.
However, the big difference is that $\vb C^{(n_f)}(z,Q^2,m^2)$ only contains a finite amount of logarithms, where as $\vb E^{(n_f+1)}$ is resumming those logarithms.
This means that for $Q^2 \gg m^2$ FFNS is indeed a bad choice as the logarithms $\ln(Q^2/m^2)$ are big and better be resummed.
Instead any power-suppressed terms, \cref{eq:Cpower}, which are important in the region $Q^2 \sim m^2$ and made FFNS preferable over ZM-VFGNS, are irrelevant in this region.

\begin{conclusionbox}[label=box:gmvfns]{GM-VFNS}
    A General Mass-Variable Flavor Number Scheme (GM-VFNS) must approximate a cross section $\sigma(x,Q^2)$
    \begin{itemize}
        \item in the region $Q^2 \sim m^2$ with the FFNS result $\sigma^{(n_f)}(x,Q^2,m^2)$
        \item in the region $Q^2 \gg m^2$ with the resummed ZM-VFNS result $\sigma^{(n_f+1)}(x,Q^2)$
    \end{itemize}
\end{conclusionbox}

\Cref{box:gmvfns} gives no exact prescription on how the approximation has to be done and, indeed, there is some freedom on how to do this.
Different PDF fitting groups make different choices~\cite{Aivazis:1993pi,Thorne:1997uu,Kramer:2000hn,Tung:2001mv,Nadolsky:2009ge,Forte:2010ta,Guzzi:2011ew,Bonvini:2016fgf,Barontini:2024xgu} and as an exemplary case we consider here FONLL~\cite{Forte:2010ta,Barontini:2024xgu}, which has a simple idea:
in order to match the two regions, we simply add the two expressions together and subtract any overlap.
Let's consider the concrete case of charm:
\begin{equation}
    \sigma^\text{FONLL}(x,Q^2,m_c^2) = \sigma^{(3)}(x,Q^2,m_c^2) + \sigma^{(4)}(x,Q^2) - \sigma^{(3\cap 4)}(x,Q^2,m_c^2)\,. \label{eq:sigmaFONLL}
\end{equation}
Here,
\begin{itemize}
    \item $\sigma^{(3)}(x,Q^2,m_c^2)$ represents the massive FFNS result, which contains power-like $Q^2/m_c^2$ terms and a finite amount of $\ln(Q^2/m_c^2)$ associated with the charm
    \item $\sigma^{(4)}(x,Q^2)$ represents the massless ZM-VFNS result, which resums all logarithms $\ln(Q^2/m_c^2)$, including the ones associated with the charm
    \item $\sigma^{(3\cap 4)}(x,Q^2,m_c^2)$ collects all terms, which appear in both expressions simultaneously, and for which we have borrowed the notation from set notation
\end{itemize}
One can show~\cite{Barontini:2024xgu} that the overlap contribution can be written as
\begin{equation}
    \sigma^{(3\cap 4)}(x,Q^2,m_c^2) = \left(\vb C^{(3\cap 4)}(Q^2,m^2)\otimes \vb f^{(3)}(Q^2)\right)(x)
\end{equation}
where the corresponding coefficient function is given by
\begin{equation}
    \vb C^{(3\cap 4),T}(z,Q^2,m^2) = \left(\vb C^{(4),T}(Q^2)\otimes \vb A^{(4)}(Q^2,m^2)\right)(x)\,,
\end{equation}
i.e.\ the right-hand-side of \cref{eq:Cmatching}.
It is immediately clear that in the limit $Q^2 \gg m^2$ the coefficient functions $\vb C^{(3),T}$ and $\vb C^{(3\cap 4),T}$ become identical and, thus, in \cref{eq:sigmaFONLL} only $\sigma^{(4)}$ contributes as requested by \cref{box:gmvfns}.
On the other side, since $\sigma^{(3\cap 4)}$ contains exactly the logarithmic terms of $\sigma^{(3)}$ and those are also contained in $\sigma^{(4)}$, which actually only contains logarithms, we also match the $Q^2 \sim m^2$ region.
The yet additional logarithms in $\sigma^{(4)}$, which are resummed there, are small in this region and a part of the approximation FONLL takes.

\subsection{Interplay with previous content}
\begin{itemize}
    \item The relevant parameter in \cref{box:gmvfns} is the scale $Q^2$, which, as we explain in \cref{sec:diverse}, is very different between various experiments.
        While for NC DIS at HERA heavy quark mass effects are very relevant and can be up to $\SI{20}{\percent}$~\cite{H1:2015ubc,H1:2018flt} in some kinematic regime, for CC DIS at HERA there are practically irrelevant since $Q^2$ is large, see \cref{tab:HERA}.
        However, when we consider CC DIS at small $Q^2$, as is present e.g.\ in neutrino experiments, they are again very relevant~\cite{Gao:2017kkx,Helenius:2026uuz,Caola:2026kvl}.
    \item At this point we can justify to neglect the top quark, since typical virtualities are below the top quark threshold, see \cref{eq:zmvfns}.
    \item The mathematical structure in massless and massive diagrams is very different, e.g.\ the former yields collinear divergencies, see \cref{sec:rsl,sec:nlo}, but the latter regulates them with explicit logarithms $\ln(Q^2/m^2)$, which makes them very different for interpolation grids, \cref{sec:grids}.
        Moreover, the massive diagrams contain far more special functions, which already makes the NLO diagrams no longer analytically solvable but only numerically tractable~\cite{Hekhorn:2019nlf}.
    \item Since the number of active flavors $n_f$ is a direct dependency of the strong coupling $\alpha_s^{(n_f)}$ and PDFs $\vb f^{(n_f)}$ it appears explicitly in scale variations, \cref{sec:sv}.
        While for the renormalization scale variation it reduces to choosing the correct $\beta_0^{(n_f)}$ in \cref{eq:CbarRimpl}, for the factorization scale variations it is more complicated as usual.
        First, it requires choosing the correct $\vb P^{(n_f)}$ in \cref{eq:CbarFNLO}, but second it also requires the correct definition of the evolution basis.
        For example, now we can identify \cref{eq:Singlet} as the four flavor singlet $f_\Sigma^{(4)}$, where as in three flavor we would get
        \begin{equation}
            f_\Sigma^{(3)}(x,Q^2) &= f_d(x,Q^2) + f_{\bar d}(x,Q^2) + f_u(x,Q^2) + f_{\bar u}(x,Q^2) + f_s(x,Q^2) + f_{\bar s}(x,Q^2)
        \end{equation}
        since, e.g., the charm is not an active quark and does not participate in \cref{eq:DGLAP}.
\end{itemize}
% F2c?
