%% Title
\titlepage[University of Jyväskylä]{Lecture notes for the Jyväskylä Summer School 2026}

%% Abstract
\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
  Due to its conceptual simplicity, Deeply Inelastic Scattering (DIS) often serves as a textbook example for Quantum Chromo Dynamics (QCD) and partonic structure of nucleons.
  However, it is this supposed simplicity, which makes DIS an ideal case for discussing many additional effects and corrections.
  In these lectures we discuss DIS within the domain of perturbative QCD covering a range of topics ranging from mathematical problems to kinematical corrections, and to practical challenges when attempting interpret experimental measurements.
  Although here we focus on the exemplary case of DIS, the discussed topcis are relevant to a larger class of processes.
  We also overview existing and future DIS measurements, and discuss their implementation into modern extractions of parton distribution functions (PDFs) which quantify the partonic structure of nucleons.

  The discussed features are all implemented in the Yadism~\cite{Candido:2024rkr,barontini_2026_18758473} open source code, which has been used for PDF extraction from a wide range of the available world data on fully inclusive DIS.
\end{abstract}


%% Declaration
% \begin{declaration}
%   This dissertation is the result of my own work, except where explicit
%   reference is made to the work of others, and has not been submitted
%   for another qualification to this or any other university. This
%   dissertation does not exceed the word limit for the respective Degree
%   Committee.
%   \vspace*{1cm}
%   \begin{flushright}
%     Andy Buckley
%   \end{flushright}
% \end{declaration}


% Acknowledgements
\begin{acknowledgements}
  First, I want to thank Werner Vogelsang, who not only introduced me into the world of pQCD, DIS, and PDFs, but who also gave me the opportunity to explore all the glorious details, which we happily neglect in the rest of this work.
  It turns out, recently, there is a renewed interest in my PhD thesis~\cite{Hekhorn:2019nlf} which discusses a fairly complicated DIS process.

  Second, I want to thank the members of the NNPDF collaboration and in particular Alessandro Candido, Giacomo Magni, and Stefano Forte, with whom I sorted out in long discussions even more details of DIS.
  Together, we have eventually brought all our experience and expertise into Yadism~\cite{Candido:2024rkr}, which, hopefully, serves the community well in the coming years.

  Third, I want to thank Ilkka Helenius and Hannu Paukkunen, who have supported me in various ways, gave me a lot freedom to work on my projects, and have shown me how to apply my knowledge to other, new fields.
  Eventually, they have also provided me with this opportunity to talk about my research and teach in front of students.

  This work has been supported by the Academy of Finland project 358090 and was funded as a part of the Center of Excellence in Quark Matter of the Academy of Finland, project 346326.
  The \LaTeX{} template is based on \texttt{hepthesis} by A.~Buckley.
  The Feynman diagrams are drawn with the \href{https://pypi.org/project/feynman/}{\texttt{feynman}} Python package.
\end{acknowledgements}


% Preface
\begin{preface}
  Here is the usual list of disclaimers:
  \begin{itemize}
    \item This is a highly personal selection of topics, which we consider relevant enough for presenting in this occasion and by no means a review of DIS, not even fully inclusive DIS in the collinear framework using pQCD, which is the only topic here.
    \item Since this is not a review also the list of reference is not exhaustive, but rather a starting point and the reader should consult the mentioned works for further references.
    \item This work may contain errors, such as typographical or grammatical, but hopefully no physical, mistakes. Their distribution and the overall normalization is currently unknown, but we hope the former is highly localized and the latter small.
  \end{itemize}
\end{preface}

%% ToC
\tableofcontents


%% Strictly optional!
% \frontquote{%
%   Writing in English is the most ingenious torture\\
%   ever devised for sins committed in previous lives.}%
%   {James Joyce}
% %% I don't want a page number on the following blank page either.
% \thispagestyle{empty}
